---
title: "Course Summary"
author: "Ziqiang Chen"
date: "October 21, 2016"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Course Summary}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Day 1: Packages and Version Control

We learned to create a package using [devtools][1]. The way to get started is
to create a skeleton of a package.

```
library(devtools)
create("Elbo")
```

This creates a directory with a couple files and a folder.
We then did the following:

1. The DESCRIPTION contains info about the package; we edited it for our purpose.
2. We looked at the NAMESPACE, but didn't touch it.
3. We created our first function in the R folder, `hi()`.

We then used [roxygen2][] to add documentation to the function, 
including inforamtion about parameters and return values.
We also used tags (`@export`) to indicate that we want to 'export' the function
from the namespace.

We also learn to manage source code with [github][].

Here's the result of our work:

```{r our-package}
library(Elbo)
hi("Ziqiang")
```


## Day 2: Classic, Rich and Tidy data

'Classic' data is represented as a `data.frame()' with sample as rows 
and feature as columns.

```{r}
pdatafl = "C:/Users/ziqiangc/Dropbox/RDevWorkshop/Elbo/ALL-phenoData.csv"
exprfl = "C:/Users/ziqiangc/Dropbox/RDevWorkshop/Elbo/ALL-expression.csv"
classic <- input_classic(pdatafl, exprfl)
classic[1:5,c(1:3, 22:24)]
```

One of the things we did was to plot the distribution of expression values across genes.
```{r classic-exprs-hist}
hist(colMeans(classic[, -(1:22)]))

```


[1]: https://cran.r-project.org/package=devtools
[roxygen2]: https://cran.r-project.org/package=roxygen2
[github]: https://github.com/


